---
title: "In Class Assignment - RMarkdown"
author: "Dr. Shoemaker"
date: "DATA 2401"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

```


Reminder: There is a "Markdown Help" page available in RStudio. 


## In-class Activity, Markdown

Below the "Your work here" section header, do the following 3 things. To turn this in, knit the RMarkdown file, and zip and submit the html.  

1. Put your favorite quote in a block quote. Add a functioning link to a website that provides more information about that quote.

2. Make a three column table of the current courses you are taking, with separate columns for course number (in __bold__), course title (in _italics_), and instructor name.

3. Lastly, make a section with some information about your favorite author or musician.

+ A _heading_ with the name of the artist or author;    
+ An example of their writing or lyrics (formatted in a *plain code block*);   
+ A _list_ of things they have written or performed (remember to use the formatting markup for a list!).     


Note that you can click "Knit" as you go along to see what the final results are going to look like. Zip the resulting html and turn it in to Blackboard.     
 
# Your Work Here! 

Remove this text and replace it with the code to do the three requests above. 
